## Key R functions used in this notebook

This page collects every new R function you used in this tutorial, in one place, as a quick-reference glossary. Each function below follows the same format:

- **Package:** where the function comes from. Most functions in this tutorial come from **dplyr**, a package for wrangling data, or **ggplot2**, a package for making charts. A few are **Base R** (built into R, no setup needed). Add-on packages must be loaded first with `library()` before you can use them.
- **What it does:** a plain-English explanation, no jargon.
- **Why you'd use it:** the everyday analyst reason you'd reach for it.
- **Arguments:** the inputs you put inside the parentheses `()` to tell the function exactly what to work on. Some are required, some are optional. Arguments listed here are not necessarily exhaustive.
- **Example:** the function used on this week's `firm_strategy` or `industry_summary` data.

For more information on any function, use ?`function_name` in the R console (e.g. `?filter`) to see the official documentation, which includes a full list of arguments, descriptions, and often many examples.

### `filter()`

**Package:** dplyr

**What it does:** Keeps only the rows that meet a condition you set, and drops the rest.

**Why you'd use it:** To narrow your dataset down to just the observations that make sense for your analysis, for example, only keeping firms where a ratio can be calculated sensibly.

**Arguments:**

- `...` — one or more conditions the kept rows must satisfy, such as `sale > 0`. You can list several conditions separated by commas; a row is kept only if all of them are true.

**Example:**

```{r}
#| eval: false
# Keep only firms with strictly positive sales and assets
firm_strategy <-
  asx_data |>
  filter(sale > 0, at > 0)
```

### `mutate()`

**Package:** dplyr

**What it does:** Creates a new column in your data, or changes an existing one, based on a calculation you specify.

**Why you'd use it:** To build new variables from ones you already have, like turning raw financial figures into ratios.

**Arguments:**

- `...` — one or more `name = calculation` pairs. `name` is what you want to call the new column, and `calculation` is the formula that creates it, such as `profit_margin = ebit / sale`.

**Example:**

```{r}
#| eval: false
firm_strategy <-
  asx_data |>
  filter(sale > 0, at > 0) |>
  mutate(
    profit_margin = ebit / sale,
    asset_turnover = sale / at
  )
```

### `select()`

**Package:** dplyr

**What it does:** Keeps only the columns you name, and drops the rest.

**Why you'd use it:** To create a smaller, easier-to-read version of your data with just the variables you need, for example when checking that new calculations look right.

**Arguments:**

- `...` — the names of the columns you want to keep, separated by commas, such as `conml, ebit, at, sale`.

**Example:**

```{r}
#| eval: false
firm_strategy_check <-
  firm_strategy |>
  select(conml, ebit, at, sale, profit_margin, asset_turnover)
```

### `arrange()`

**Package:** dplyr

**What it does:** Sorts the rows of your data by one or more columns.

**Why you'd use it:** To rank observations from lowest to highest, or highest to lowest with `desc()`, so you can see which rows stand out.

**Arguments:**

- `...` — the column(s) to sort by. By default, sorting goes from lowest to highest; wrap a column in `desc()` to sort from highest to lowest.

**Example:**

```{r}
#| eval: false
industry_summary |>
  filter(n_firms >= 3) |>
  arrange(desc(avg_profit_margin))
```

### `slice_max()`

**Package:** dplyr

**What it does:** Keeps only the rows with the highest values of a column you choose.

**Why you'd use it:** To quickly pull out the top performers, for example the five firms with the highest profit margin.

**Arguments:**

- `order_by` — the column whose highest values you want, such as `profit_margin`.
- `n` — how many rows to keep, such as `n = 5`.

**Example:**

```{r}
#| eval: false
firm_strategy |>
  slice_max(profit_margin, n = 5) |>
  select(conml, industry, profit_margin, asset_turnover)
```

### `group_by()`

**Package:** dplyr

**What it does:** Splits your data into groups based on the values of one or more columns, without changing what the data looks like on screen.

**Why you'd use it:** To set up the data so that a later step, usually `summarise()`, calculates results separately for each group, such as each industry.

**Arguments:**

- `...` — the column(s) to group by, such as `industry`.

**Example:**

```{r}
#| eval: false
industry_summary <-
  firm_strategy |>
  group_by(industry)
```

### `summarise()`

**Package:** dplyr

**What it does:** Collapses many rows into a single summary row, using calculations you choose, such as an average.

**Why you'd use it:** To go from firm-level detail to industry-level patterns, condensing hundreds of rows into one row per group.

**Arguments:**

- `...` — one or more `name = calculation` pairs, such as `avg_profit_margin = mean(profit_margin, na.rm = TRUE)`. If the data was grouped with `group_by()` first, one row is produced per group.

**Example:**

```{r}
#| eval: false
industry_summary <-
  firm_strategy |>
  group_by(industry) |>
  summarise(
    n_firms = n(),
    avg_profit_margin = mean(profit_margin, na.rm = TRUE),
    avg_asset_turnover = mean(asset_turnover, na.rm = TRUE)
  )
```

### `slice_head()`

**Package:** dplyr

**What it does:** Shows the first few rows of your data, in the order they currently appear.

**Why you'd use it:** To preview a dataset without printing every row, handy for checking that a new variable looks right.

**Arguments:**

- `n` — how many rows to show, such as `n = 10`.

**Example:**

```{r}
#| eval: false
firm_strategy_check |>
  slice_head(n = 10)
```

### `n()`

**Package:** dplyr

**What it does:** Counts how many rows are in the current group.

**Why you'd use it:** Used inside `summarise()` to record how many observations, such as firms, make up each group.

**Arguments:**

- none. `n()` takes no arguments; it simply counts the rows it is given.

**Example:**

```{r}
#| eval: false
industry_summary <-
  firm_strategy |>
  group_by(industry) |>
  summarise(n_firms = n())
```

### `mean()`

**Package:** Base R

**What it does:** Calculates the average of a set of numbers.

**Why you'd use it:** To summarise a whole column of values, such as profit margin, with a single typical value.

**Arguments:**

- `x` — the numeric column you want to average, such as `profit_margin`.
- `na.rm` — *(optional)* set to `TRUE` to ignore missing values when calculating the average. If you leave this out and there are missing values, the result will be `NA`.

**Example:**

```{r}
#| eval: false
mean(firm_strategy$profit_margin, na.rm = TRUE)
```

### `desc()`

**Package:** dplyr

**What it does:** Flags a column so that `arrange()` sorts it from highest to lowest instead of lowest to highest.

**Why you'd use it:** To rank firms or industries from best to worst on a chosen measure, such as ranking industries from highest to lowest average profit margin.

**Arguments:**

- `x` — the column you want sorted in descending order, such as `avg_profit_margin`.

**Example:**

```{r}
#| eval: false
industry_summary |>
  arrange(desc(avg_profit_margin))
```

### `geom_point()`

**Package:** ggplot2

**What it does:** Adds a layer of points to a plot, creating a scatter plot.

**Why you'd use it:** To see the relationship between two numeric variables, such as average profit margin and average asset turnover across industries.

**Arguments:**

- none used in this tutorial. `geom_point()` is added on its own, using the x and y mapping already set in `aes()`.

**Example:**

```{r}
#| eval: false
industry_summary |>
  ggplot(aes(x = avg_profit_margin, y = avg_asset_turnover)) +
  geom_point()
```
