<!-- question-type: inclass -->
### Exercise 8 [Optional]: Counting Firms Above and Below the Median Profit Margin

So far, we have used averages to compare industries. Another useful question is whether an industry has many firms performing above a simple benchmark, or only a small number of standout firms. In this exercise, we use the median profit margin as that benchmark and count how many firms in each industry fall above and below it.

**(a).** First, compute the median of `profit_margin` and store it in an object called `median_profit_margin`.

```{r}
#| eval: false
median_profit_margin <- median(YOUR_CODE_HERE, na.rm = TRUE)
```

**(b).** Now use `mutate()` and `if_else()` to create a new variable called `margin_groip`.

Classify firms as:

* `"Above median margin"` if `profit_margin >= median_profit_margin`
* `"Below median margin"` otherwise

```{r}
#| eval: false
firm_strategy_bucketed <-
    firm_strategy |>
    mutate(
        margin_group = if_else(
            profit_margin >= YOUR_CODE_HERE,
            "Above median margin",
            "Below median margin"
        )
    )
```

**(c).** Using `group_by()` and `summarise()`, count how many firms fall into each combination of `industry` and `margin_group`.

```{r}
#| eval: false
firm_strategy_grouped |>
    group_by(YOUR_VARIABLES_HERE) |>
    summarise(YOUR_CODE_HERE)
```

**(d).** Now produce the same result using `count()` by running the code below.

```{r}
#| eval: false
firm_strategy_grouped |>
    count(industry, margin_bucket, name = "n_firms")
```

**(e).** Compare the code from parts (c) and (d). What does this suggest about when `count()` might be useful?

**(f).** Looking at your table, which industries appear most often in the `"Above median margin"` group?

<!-- BEGIN PROFILE:r-teaching-guide -->

::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective**

Students should:

* compute a benchmark outside the pipeline and then use it inside `mutate()`
* use `if_else()` to create a simple two-group categorical variable
* apply `group_by()` and `summarise(n = n())` to count grouped observations
* recognise that `count()` is a convenient shortcut for a common grouped counting task
* interpret counts above and below a benchmark as a different way of comparing industries

✅ **Core Concepts to Highlight**

* Averages are useful, but they do not show how observations are distributed within a group
* The median can be used as a simple benchmark to split firms into two categories
* It can be helpful to calculate a benchmark outside the pipeline and then refer to it inside `mutate()`
* `if_else()` creates a new variable based on a condition
* `group_by(industry, margin_group)` combined with `summarise(n_firms = n())` counts firms in each combination
* `count(industry, margin_group)` is a shorter way to do a similar task
* This exercise shows a composition-based view of industries, not just an average-based view

💬 **Suggested In-Class Prompts**

* What does this exercise tell us that an industry average does not?
* Why might an industry with a high average margin still have only a few firms above the median?
* Why might it be useful to calculate the median once and store it as an object?
* What is the role of the median in this exercise?
* How does `count()` relate to `group_by()` and `summarise(n = n())`?
* Why might an analyst choose the shorter `count()` version in practice?

📌 **Common Misunderstandings**

* Confusing the median benchmark with the industry average
* Trying to put too much new logic into one line instead of using a stored object to simplify the code
* Forgetting to include both `industry` and `margin_group` in the grouped count
* Thinking `count()` does something conceptually different from `summarise(n = n())`
* Interpreting raw counts as proportions or shares
* Forgetting that industries with more firms may naturally appear more often in the counts

:::

:::

:::

<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->

::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

**(a).** Compute the median of `profit_margin` and store it in an object.

```{r}
median_profit_margin <- median(firm_strategy$profit_margin, na.rm = TRUE)
```

**(b).** Create `margin_bucket` using `mutate()` and `if_else()`.

```{r}
firm_strategy_grouped <-
    firm_strategy |>
    mutate(
        margin_bucket = if_else(
            profit_margin >= median_profit_margin,
            "Above median margin",
            "Below median margin"
        )
    )
```

**(c).** Count firms using `group_by()` and `summarise()`.

```{r}
firm_strategy_grouped |>
    group_by(industry, margin_bucket) |>
    summarise(n_firms = n(), .groups = "drop")
```

**(d).** Produce the same result using `count()`.

```{r}
firm_strategy_grouped |>
    count(industry, margin_bucket, name = "n_firms")
```

**(e).** One possible interpretation is:

* The two pieces of code produce the same type of result.
* `count()` is useful when we want a quick grouped frequency table without writing out `group_by()` and `summarise(n_firms = n())` in full.
* `group_by()` and `summarise()` are more flexible, while `count()` is a helpful shortcut for a common task.

**(f).** A good answer should name the industries that appear most often in the `"Above median margin"` group and note that this is a different way of comparing industries from using averages alone.

:::

:::

:::

<!-- END PROFILE:r-solutions -->
  