<!-- question-type: prepare -->
### Exercise 3: Create the Analysis Dataset

In the rest of this tutorial, we will work with a dataset called `firm_strategy`.
To create `firm_strategy`, we need to construct some variables from the ASX dataset.

**(a).** Load the ASX data located in `data/asx_200_2024.csv` into an object called `asx_data`.

```{r}
#| eval: false
asx_data <- YOUR_CODE_HERE
```

**(b).** We now want to create a new dataset called `firm_strategy` from `asx_data`.

To do this, we need to:

1. keep only firms for which the ratios can be calculated sensibly, and
2. create two new variables:

   * `profit_margin`
   * `asset_turnover`

Before writing any code, look at the formulas for these variables and think about which original variables must be **strictly positive**.

**(c).** Use your answer to complete the code below. Replace `YOUR_CONDITIONS` and fill in the two missing ratio definitions.

```{r}
#| eval: false
firm_strategy <-
    asx_data |>
    filter(YOUR_CONDITIONS) |>
    YOUR_CODE_HERE(
        profit_margin = YOUR_CODE_HERE,
        asset_turnover = YOUR_CODE_HERE
    )
```

**(d).** In one sentence, explain why we use `filter()` before `mutate()` in our solution to (c).

<!-- BEGIN PROFILE:r-teaching-guide -->

::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective**

Students should:

* load the original ASX dataset into R
* recognise that a new analysis dataset is created by transforming an existing dataset
* infer the filter conditions needed before calculating ratios
* use `filter()` and `mutate()` together in a simple pipeline

✅ **Core Concepts to Highlight**

* We often create a new working dataset from a larger original dataset
* Ratio variables require attention to their denominators
* If a denominator is zero or negative, the resulting ratio may be undefined or misleading for this exercise
* `filter()` keeps only the rows we want to work with
* `mutate()` creates new variables from existing ones
* The order of operations matters: we first keep valid rows, then calculate the new variables

💬 **Suggested In-Class Prompts**

* Which original variables appear in the denominators of the three ratios?
* Why do we need to think about the denominator before calculating a ratio?
* What problem could arise if `sale`, `at` were zero?
* Why is it useful to save the result as a new object like `firm_strategy` rather than overwriting the original data?

📌 **Common Misunderstandings**

* Forgetting that the ratio conditions come from the denominators, not the numerators
* Allowing zero values when the exercise is asking for ratios to be calculated sensibly
* Confusing the original dataset (`asx_data`) with the new derived dataset (`firm_strategy`)
* Thinking `mutate()` automatically removes invalid rows

:::

:::

:::

<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->

::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

**(a).** Load the ASX data into an object called `asx_data`.

```{r}
asx_data <- 
  read_csv("data/asx_200_2024.csv")
```

**(b).** The variables that must be strictly positive are the ones in the denominators of the ratios:

* `sale` for `profit_margin`
* `at` for `asset_turnover`

**(c).** One correct completed version is:

```{r}
firm_strategy <-
    asx_data |>
    filter(sale > 0, at > 0) |>
    mutate(
        profit_margin = ebit / sale,
        asset_turnover = sale / at
    )
```

**(d).** One possible answer is:

> We use `filter()` before `mutate()` so that we only calculate the ratios for firms where the denominators are valid.

:::

:::

:::

<!-- END PROFILE:r-solutions -->
