<!-- question-type: inclass -->
### Exercise 5: Which Firms Rely Most on Margin? Which Rely Most on Volume?

Some firms generate strong profits from each dollar of sales. Others generate large sales from a given asset base. In this exercise, we compare firms at the top of each of these two dimensions.

**(a).** Use `slice_max()` to identify the five firms with the highest `profit_margin`.

Your table should include:

* `conml`
* `industry`
* `ebit`
* `at`
* `sale`
* `profit_margin`
* `asset_turnover`

```{r}
#| eval: false
firm_strategy |>
    slice_max(YOUR_CODE_HERE) |>
    select(YOUR_VARIABLES_HERE)
```

**(b).** Now produce the equivalent table for the five firms with the highest `asset_turnover`.

```{r}
#| eval: false
firm_strategy |>
    slice_max(YOUR_CODE_HERE) |>
    select(YOUR_VARIABLES_HERE)
```

**(c).** Compare the two tables.

* Do the same firms appear in both tables?
* What kinds of industries seem more common in each table?
* What does this suggest about different ways firms generate profits?

<!-- BEGIN PROFILE:r-teaching-guide -->

::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective**

Students should:

* use `slice_max()` to identify firms at the top of a chosen variable
* compare firms that perform strongly on different dimensions of strategy
* interpret the difference between high profit margin and high asset turnover in business terms
* recognise that firms can generate strong performance in different ways

✅ **Core Concepts to Highlight**

* `slice_max()` keeps the rows with the highest values of a chosen variable
* `profit_margin` and `asset_turnover` capture different dimensions of firm strategy
* high profit margin means earning more profit per dollar of sales
* high asset turnover means generating more sales from a given asset base
* comparing the two tables helps students see that firms can succeed through different business models

💬 **Suggested In-Class Prompts**

* What is the difference between being high-margin and high-volume?
* Do you expect the same firms to appear in both tables? Why or why not?
* Which industries seem more common among high-margin firms?
* Which industries seem more common among high-turnover firms?
* Why might mining or utilities produce higher margins than retail or distribution?
* Why might retail, services, or engineering produce higher turnover than mining or utilities?
* What does this comparison suggest about different ways of generating profits?

📌 **Common Misunderstandings**

* Thinking that firms with high profit margins must also have high asset turnover
* Forgetting that `slice_max()` keeps rows rather than sorting the entire dataset
* Interpreting profit margin and asset turnover as the same kind of performance measure
* Focusing only on firm names and not on broader industry patterns

:::

:::

:::

<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->

::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

**(a).** Use `slice_max()` to identify the five firms with the highest `profit_margin`.

```{r}
firm_strategy |>
    slice_max(profit_margin, n = 5) |>
    select(conml, industry, profit_margin, asset_turnover)
```

**(b).** Produce the equivalent table for the five firms with the highest `asset_turnover`.

```{r}
firm_strategy |>
    slice_max(asset_turnover, n = 5) |>
    select(conml, industry, profit_margin, asset_turnover)
```

**(c).** One possible interpretation is:

* The same firms do **not** appear in both tables, which suggests that high profit margin and high asset turnover capture different ways of operating.
* Firms in the high-margin table earn more profit from each dollar of sales. These firms may benefit from pricing power, favourable cost conditions, scarce resources, or stable demand.
* In this output, the high-margin table includes industries such as **mining**, **gas utilities**, and **building products**.
* This makes economic sense because some firms in these sectors can earn strong margins without needing extremely high sales relative to their asset base.
* Firms in the high-turnover table generate more sales from a given asset base. These firms may rely more on high volume, fast-moving sales, or relatively asset-light operations.
* In this output, the high-turnover table includes industries such as **professional services**, **specialty retail**, **commercial services**, **construction and engineering**, and **distribution/retail**.
* This also makes sense because firms in these sectors often operate by generating lots of sales or work relative to the assets recorded on their balance sheets.
* The broader lesson is that firms can generate strong performance in different ways: some rely more on margin, while others rely more on turning assets into sales quickly.
* A useful intuition is that a mining firm may sell fewer units but earn much more on each sale, while a retailer may earn much less on each sale but sell many more units.

In the next exercise we will see how this relates to industry sectors as a whole.

:::

:::

:::

<!-- END PROFILE:r-solutions -->

