<!-- question-type: prepare -->
### Exercise 4: Create a Smaller Checking Dataset

We have now created a new dataset called `firm_strategy`.
Before moving on, it is good practice to check that the new variables were created correctly.
One useful way to do this is to create a smaller dataset that contains only the variables we need for checking.

**(a).** Create a new object called `firm_strategy_check` that keeps only the following variables:

* `conml`
* `ebit`
* `at`
* `sale`
* `profit_margin`
* `asset_turnover`

```{r}
#| eval: false
firm_strategy_check <-
  firm_strategy |>
  YOUR_FUNCTION(YOUR_VARIABLES)
```


**(b).** Display the first 10 rows of `firm_strategy_check`. You may find the command `slice_head(n = 10)` helpful here.

```{r}
#| eval: false
firm_strategy_check |>
  YOUR_CODE
```

**(c).** Why might it be useful to create a smaller checking dataset instead of inspecting the full `firm_strategy` dataset?

**(d).** Looking at a few rows is a useful first step, but it might not scale well to a large dataset where we compute hundreds of variables. What might be a more scalable next step if you wanted to check whether `profit_margin` and `asset_turnover` look reasonable across all firms?

<!-- BEGIN PROFILE:r-teaching-guide -->

::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective**

Students should:

* use `select()` to create a smaller dataset for checking work
* use `slice_head()` to inspect a manageable number of rows
* understand why analysts often reduce a dataset before checking calculated variables
* explain why row-level inspection is only a first check and why more scalable summary-based checks are useful

✅ **Core Concepts to Highlight**

* Checking work is an important part of data analysis
* A smaller dataset can make inspection easier by removing irrelevant columns
* `select()` reduces the columns to just the variables we need
* `slice_head()` helps us inspect a small number of rows without printing the full dataset
* Looking at a few rows is a useful first check, but larger datasets often require summary-based checks as well

💬 **Suggested In-Class Prompts**

* Why is it often easier to inspect a narrow table than a full dataset?
* Which original variables do we need to check `profit_margin`?
* Which original variables do we need to check `asset_turnover`?
* Why might we inspect a few rows first instead of all rows at once?
* What could we do next if we wanted a more scalable check across all firms?
* What does this exercise teach us about good analytical workflow?

📌 **Common Misunderstandings**

* Thinking that checking work means printing the entire dataset
* Forgetting to keep the original variables needed to verify the new ratios
* Treating `slice_head()` as a way to summarise the data rather than just inspect a few observations
* Giving vague answers about “checking” without suggesting a more scalable next step such as summary statistics

:::

:::

:::

<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->

::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

**(a).** Create a new object called `firm_strategy_check` that keeps only the listed variables.

```{r}
firm_strategy_check <-
    firm_strategy |>
    select(conml, ebit, at, sale, profit_margin, asset_turnover)
```

**(b).** Display the first 10 rows.

```{r}
firm_strategy_check |>
    slice_head(n = 10)
```

**(c).** One possible answer is:

> A smaller checking dataset makes it easier to focus only on the variables needed to verify the new calculations.

**(d).** One possible answer is:

> A more scalable next step would be to create summary statistics for the new variables so we can check their overall patterns and identify unusual or extreme values.

:::

:::

:::

<!-- END PROFILE:r-solutions -->
