## The Business Challenge

```{r}
#| warning: false
#| echo: false
library(tidyverse)
```

```{r}
#| warning: false
#| eval: true
#| echo: false
#| cache: true

# Create data/ directory if it doesn't exist
if (!dir.exists("data")) {
  dir.create("data")
}
# Define URL and destination file path
url <- "https://raw.githubusercontent.com/unimelb-cmce-10002/fba-book/refs/heads/main/data/asx_200_2024.csv"
destfile <- "data/asx_200_2024.csv"
# Download the file if it doesn't already exist
if (!file.exists(destfile)) {
  download.file(url, destfile, mode = "wb")
}
```

### The Topic: Understanding firm strategy in the Australian economy {.unnumbered}

Firms can generate strong results in different ways. One firm may earn a lot of profit from each dollar of sales. Another may earn less on each sale, but generate very high sales relative to the assets it uses. These are different ways of operating, and they often reflect differences in business model and industry structure.

In this tutorial, we focus on two measures:

$$
\mathrm{Profit\ Margin} = \frac{\mathrm{EBIT}}{\mathrm{Sales}}
$$

$$
\mathrm{Asset\ Turnover} = \frac{\mathrm{Sales}}{\mathrm{Assets}}
$$

These measures help us think about two different dimensions of performance:

* **Profit margin** tells us how much profit a firm earns from each dollar of sales
* **Asset turnover** tells us how effectively a firm turns its asset base into sales

Using `dplyr`, we will create these variables, check that they were calculated correctly, and then use them to answer a series of business questions.

In particular, we will ask:

* Which firms appear strongest on **profit margin**, and which appear strongest on **asset turnover**?
* Do the same firms appear at the top of both rankings, or do different firms succeed in different ways?
* When we move from individual firms to industries, do the same patterns still appear?
* Do some industries seem to rely more on **high margins**, while others rely more on **high turnover**?
* What do these patterns suggest about how executives should interpret firm performance?

By the end of the tutorial, you should be able to use `dplyr` to turn raw accounting data into a short executive-style summary of how firms and industries generate strong results.

### The Data: Financial Statement Observations from Yahoo Finance{.unnumbered}

To answer these questions, we draw on audited 2024 financial statements for the 200 largest ASX-listed firms (as measured by assets).

Financial statements provide a standardised snapshot of a company’s performance and financial health. In our data set, the key variables are:  

- Company name (`conml`) – the name of the firm as listed on the ASX  
- Industry (`industry`) – the industry classification, allowing comparison across sectors such as mining, banking, or healthcare  
- Profit (`ebit`) – earnings before interest and taxes, representing core business profit after expenses (from the income statement)  
- Assets (`at`) – the total resources the company owns that have economic value (from the balance sheet)  
- Invested Capital (`invested_capital`) – the total capital invested in the company by both shareholders and debt holders to fund operations and growth. It generally includes:  

By working with these statements and variables, we can replicate the kind of assessments that professional analysts and fund managers use to guide billion-dollar investment decisions.  

As you will see, just a few lines of R code can wrangle raw financial statements information into orderly data summaries that allow us to understand how businesses across different industry sectors perform across various metrics.

## R packages for today {.unnumbered}

```{r}
#| eval: false
library(tidyverse)     # collection of packages for data manipulation and visualization
```

